\documentclass[11pt,a4paper,sans]{moderncv}
% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{black}


\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}
%% Character encoding
\usepackage[utf8]{inputenc}
%% Adjust the page margins
\usepackage[scale=0.75]{geometry}
%% Personal data
\firstname{Caleb}
\familyname{Everett}
\address{63 Villa Ave}{08071 Pitman New Jersey}
\mobile{1-609-670-5137}
\email{everett.caleb@gmail.com}
\social[github]{everett1992}
%\social[linkedin]{everett1992}

\begin{document}

\makecvtitle
\section{Education}
\cventry{2010--2014}{Computer Science}{The College Of New Jersey}{Ewing New Jersey}{}{}
\cvlistdoubleitem{Network Security}                 {Data Structures and Databases}
\cvlistdoubleitem{Programming Languages and Design} {Computer Architecture}
\cvlistdoubleitem{Cloud Computing}                  {Operating Systems}
\cvlistdoubleitem{Analysis of Algorithms}           {Human Computer Interaction}

\section{Experience}
\cventry{2010}{Student Project}{FSP Scheduler}{}{\emph{C++}}
{
  In a freshman programming class I created a scheduler used by my
  school to place freshmen into one of their three chosen (FSP) Freshmen
  Seminar Classes.
  The scheduler kept class sizes consistent while placing students in
  their highest rated classes and replaced the manual process they used to
  schedule FSPs. It used a genetic algorithm to find an optimal schedule
  for all students.
}
\cventry{2010--2012}{Software Developer Intern}{BC Processing}{}{\emph{Ruby on Rails}}
{
  This was my first technical job and I became familiar with Ruby, Rails,
  Javascript, and HTML. Prior to my first summer there I was not familiar
  with web development and I had never released any software. Three months
  later I had learned how to build and release whole Rails applications.
}
\cventry{Summer 2013}{Software Developer Intern}{Amazon.com}{}{\emph{Java}}
{
  I worked on Java and Groovy based web applications that help to identify
  and secure high value inventory items. I improved the manual process used
  to identify high value items by making the web application more robust,
  and I helped to implement a rule based automatic classifier.
}

\section{Languages and Technologies}
\cvlistdoubleitem{Ruby, Ruby on Rails} {HTML, Javascript, CSS}
\cvlistdoubleitem{Unix tools (Git, Vim, Bash)} {Amazon Web Services}
\cvlistdoubleitem{Java, Groovy, Scala} {SQL}
\cvlistdoubleitem{Bash} {C++}
\cvlistdoubleitem{Python} {Haskell}


\end{document}
